\documentclass{article}
\begin{document}


I don't know what it is about me that these girls like, but man am I enjoying it! At first, when I woke up in morning and first saw my great buchou Rias by my side, I just thought that maybe it was going to be a typical morning. What I found was completely different.

As I opened my eyes and tried to sit up in bed, I was stood shocked. there, in my bed, lied FOUR different naked women's bodies in my room (how I know this, you do not want to know). I was dumfounded. I mean, not only was the great and sexy Rias there, but the cute Asia were directly in my line of sight. This was because each of them had flanked me on both sides, with a tight grip on both of my arms (Rias to my left and Asia to my right). As I struggled to get up and see the other two culprits, their grips became stronger, as if they were in a dream where they were fighting over me. \emph{Oh, how I wish that were made reality}, I subconsciously thought.

I got up just enough to see that the final two culprits were Xenovia and Akeno. what was weird about these two was their position. They were arranged in such a way that their heads were laying just above my crotch. \emph{Good God why do they have to lay their heads next to mine}. Yet, at the same time, I kind of like the view, and considering both of them had pretty sizable breasts, from where I was precariously sitting, I had a full view of their enormous racks. As soon as I tried moving my legs, both Xenovia and Akeno started to pry my legs and place them closer to their bodies. I had to admit that despite the uncomfortable position I was in, I didn't mind it at all. Then there was a voice I really did not want to hear.

"Issei, get up!". It was my mother, and from the sound of her voice, she was close. REALLY close.

I struggled to get up, and as I squirmed, so did the girls. In a matter of minutes, my buchou Rias opened her eyes very slowly. "Issei, you're going to be late, so you better get up now," shouted my mother from the hallway. She seemed to be unaware that most of our "guests" are IN MY ROOM! I was trying to asses the situation, and figure out what to do. In that instance, I heard a voice from right next to me.

"Morning, Isse." It was Rias, and she was obviously wide awake. And as I turned around to look at her, I noticed she was in the strangest of positions; she was lying in such a way that she still had a grip on my arms, but also in a way that looked really seductive. What made it so was the fact that she had her boobs pressed up against my arm and they were being crushed by both that and both of her arms, making them look even bigger and fuller. \emph{Holy crap, don't nosebleed, not now.} "Help me get the others up," I told Rias, "and go to change in your own rooms." "As you wish," she replied, "but just know that next time I find you in this situation, I'm blaming it on you." As she said this, she motioned to the group in such a way that it looked like she wanted to kill the others.

Oh, how jealousy can work in you favor, now can it?

As we woke the others, I started to wonder why they were attracted to me. I'm not particularly good-looking, nor am I muscular. I'm just you average looking 17 year old guy. Then, a memory came to me. It was a night a few weeks before my battle with Raiser, Rias' then fiancée. I was conversing with my dear friend Ddraig, aka the Red Dragon Emperor, and the inhabitant of my Sacred Gear. The topic arose of what my goal was in life. I told him that my main goal was to become a High-Class devil and therefore Harem King. While being reluctant to admit it, he mentioned that all of his past hosts had acquired many partners, especially his male hosts. And while I don't want to admit it, if it wasn't for him, I probably would never had met Rias and the gang. I would have just died at the hands of Raynaire (remember the fallen angel I mentioned?) and have stayed dead.

"Isse, are you all right?"

This question brought me out of my daze. It was Rias. I was shocked at the tone of the question, it wasn't her usual peppy tone she uses around me. What's more was that she had a rather concerned look in her eyes. \emph{Not good}, my subconscious told me, \emph{try to lighten the mood; make her feel better}. "Yeah, I'm good," I told her, "Don't worry about me." As soon as I said this, her face seemed to relax a little, and he usual grin was my response. "Alright then, pretty boy. I'll see you in the kitchen," was all she said. With that, she pushed out all the other girls, who were already awake, and closed the door tightly behind them.

At first, I was a little relieved that they were gone. I mean, despite enjoying the fact that these girls were in my room NAKED, I still felt that I needed my own personal space sometimes. Then there was a question of why I dozed off the way I did. The way Rias looked at me once I came back made me hope that what happened now would NOT happen again in her presence. After I silently scolded myself, I got out my uniform and underclothes and left them on the bed so I can go take a shower. After my quick little shower, I changed and went downstairs with my bag to the kitchen.

Although all five of the girls were there, and I desperately was wishing otherwise, at least I got to see all of them on a daily basis. "Morning, everyone," I said, "hope everyone slept well." The general responses of "Good morning" spread quickly, and before I knew it, breakfast was over and we were all headed to school.

"So, Issei, I wanted to talk about what was on your mind earlier." Surprisingly, I hadn't noticed that Rias and I were ahead of the others. When I looked at her face, I saw the same face that she made this morning, the one filled with concern. "So, I want to know what had happened this morning. What made you doze off like that?" She asked this with a concerned, almost begging tone.

I didn't know what to say for two reasons. The first one is because I didn't want to worry her. I felt that my problems weren't anything that I should get the gang involved in. The other, more important reason, is that I don't really know myself. so I stood there, wondering what to say. Finally, I just responded with a simple answer. "I don't know. I guess I had too much on my mind," I said as if in deep thought.

"Oh, well, if its just that then," was all she replied. At first, I thought that she was happy that I was alright with my answer. Yet, the face she was making was another story; a mix of both puzzlement and disappointment. Wait, did I read that right? There was a look of stark disappointment on her face, as if she was expecting me to say something else. \emph{Maybe she wanted a different answer?} In a way, I was grateful. At least it shows that she cares. Yet, I guess I'm wondering what she expected me to say.

As we crossed the entryway to the school (yeah, the walk was that quick), I heard buchou's voice emanating from the hallway as she went to her first class. "I'll see you later, I guess," she said, disconcertedly. By the way she said it, it made me wonder what she wants from me. My only guess now as I get to class is, what will it mean for me. I guess I'll just wait and see.

\end{document}