\documentclass{article}
\begin{document}
The day went by more slowly then it normally would. P.E. was more of a pain in the ass than usual. I nearly knocked out in Math class, and I had this really tough lab in my Chemistry class. The only thing keeping me alive and going through the day was my thoughts over what Rias said to me earlier \emph{" '...I want to know what had happened this morning. What made you doze off like that?'… 'Oh, I guess if that's it, then'…'I'll see you later I guess'"}. These simple statements kept rolling around in my head and I was left wondering \emph{"Why?"}.

Why was Rias acting like this? Was something wrong and she didn't want to tell me? What was it about my responses that made her feel bad, even disappointed? These questions kept bothering me, yet I didn't want to ask them. I guess I was afraid of what her answers were. I'm not going to lie, I'm just stark scared of what she might tell me. I mean, I love her with all my heart, yet she still scares me. I mean, it isn't everyday that you hang out with a high-class devil nicknamed "The Red Haired Princess of Ruin" among her peers. That's just stark scary.

Anyway, as soon as the bell rang, I was out the classroom door, past the double doors of the school, and headed straight towards my Club's headquarters.

The building itself is pretty old. Back before the club was established. it used to be one of the school's residence halls. Now abandoned of the purpose, it became the club's headquarters. As I came closer to my destination, I started to notice the finer details of the building. The long vines growing on the façade. Some cracks on the paint and holes in the foundation made it look even older and beat up than it actually was. The inside of the building looked old, but in a preserved antique kind of way. Maybe because it was so much cleaner than the outside.

As I went in to the club's main room, I oddly felt like this was home. In front of me, the room was lit enough for people to see while inside the room, but not enough to be seen from the outside. There were two couches looking at each other with a rectangular coffee table in the middle. At the farthest end of the room facing the doors was a very sophisticated desk. That was buchou's desk, the place she takes when we're going through club activities.

On one of the couches, Gasper, the half vampire, half demon that generally lived in the old building, was sitting in his old box playing video games (ironically my game system that I let him keep0. Beside him, Koneko was sitting beside him and eating what looked like a chocolate bar. On the other couch , Kiba is sitting on the couch along with Asia, who is reading from what looks like a history textbook.

"Hey, everybody, how ya doing?" I asked. Everyone responded with a general concensus of fine. " So, where's Rias?" I asked the group. "She's in the club shower," said Akeno from out of nowhere. I jumped in my shoes a little when I heard her, but then I saw her appear from behind me. "She'll be out in a minute, Issei." That sort of gave me a sense of relief, then a sense of worry about what would happen tonight. Ignoring those thoughts, I took a seat next to Gasper and chatted with him about how he was doing.

I don't know what it is about a woman's sense of time, but it was just as Akeno said. In just a few minutes (maybe five to ten?) Rias was out of the club shower and in a bath towel. I guess she had no sense of embarrassment here, because she was completely nude under there, and from the look of that towel, it would fall off at any moment. I mean, I could make out the rim of her boobs without even trying to look. However, I was stunned at how they glistened in the dim light. Since the towel was too small, it just made her body look more voluptuous than it already was. \emph{Damn it, not again}, my mind screamed, \emph{don't nosebleed. Now is not the time nor the place!} "Just give me a couple minutes to change, then we'll get started," said Rias as she walked back into the shower room.

While she changed, I decided to get to work on some other stuff. I took out my science textbook and decide to do the homework for once. There was a big test, and I wasn't exactly sure that my parents were ready to see another F. In fact, I think that another F may equal less time with the girls, and that is something I just cannot afford.

Right when I was about to get started though, Rias came out of the shower room in her usual school uniform. At first, disappointment washed over me. I got the sensation that, for some strange ass reason, I wanted to see more. \emph{Looks like the perversion got to you}, my conscience told me, \emph{as usual, you horny bastard}. While I internally scolded myself. Rias began with her club activities. "Now then, lets go through how many pacts we've completed this week," she said.

In an instant, I perked up. I was worried that I hadn't done enough work. I mean, I helped out the others and did some of their jobs, but I wasn't able to make any of my own pacts. "Let's see. Kiba has completed 5 this week. Koneko, you completed 8. Xenovia, you completed a good 4 pacts. Asia, you got 5. Gasper, you got 10 done this week, and Akeno, you completed 7 pacts." As Rias clarified this, one by one all of the others confirmed that they did indeed complete them.

"Now, Issei...," said Rias. "So far, you've only been able to get one pact. Although this is greater than your usual haul of zero, I'm beginning to wonder why?" The stern look on her face is what scared me the most. I mean, I knew that I was on her good side (a little more about that later), but I didn't like when she gave me that face. It makes me feel rotten, almost disgusted with myself. "Well, you see buchou, I don't really know how to truly get into the subject of pacts. I mean, I know what I'm supposed to do when I'm in one, yet I don't really know how to make a new one." I don't know if what I said made sense, but the only thing that Rias did after that is laugh inwardly, as if suppressing it. \emph{What did I say that made her laugh?}

As if reading my thoughts, Rias gave me that answer, "Oh, Issei, what am I going to do with you?" In an instant, she gets up from her spot on the desk, and moves to grab me in a sort of half hug behind me. Because she had to bend over the couch, her boobs sort of just dipped low around the back of my head. The supple skin that was now this close to me made me get goose bumps all over. \emph{Damn you, you perverted mind}, I scolded my self, \emph{why do you have to get this aroused! Shit!} As my I finished scolding myself, Rias got ever so closer to my ear. When she was right next to my ear, she whispered in the most seductive way possible, "Hopefully we won't have this same problem tonight, now would we?"

In an instant, I felt a rush of blood go to my ears and my "third leg". I don't know what it is about what she just said that turned me on, but next thing I know, I'm just drooling in my head, just trying to decipher every word she just said. \emph{Damn you, Rias! Why do you tease me so!}

In a couple of minutes, this flash of what I can only describe as pure lust left my system. Although I still wanted to see what Rias meant, the feeling of lust just went away, leaving a gaping hole in my psyche. A part of me wished she had given me more (insight, that is), yet another part of me just wanted to know why she did that so suddenly.

We continued through club activities, almost as if that incident had never happened. We talked about what we would do in case of another stray devil incident (boring) and about me, Asia's, and Xenovia's latest training exercises (a pain in the ass, but I managed to convince Rias to continue training starting at six and not at five in the morning, much to her dismay).

Slowly, but surely, I came realize that Rias has her own demons inside. I don't know exactly what that was, but I knew that feeling wasn't a good one. That night, I couldn't sleep well. I was restless, tossing and turning, wanting to know what Rias is feeling. I don't know when I fell asleep, but when I did, I noticed that the only one that came beside me tonight was Rias.

In a way, her sleeping form looked so innocent. She looked almost like a pre-teen, maybe 12-14 years old at the most. I mean, I knew she was seventeen, and that people look younger when they sleep, but this was an astoundingly large difference. Not only did she look younger, but she seemed to be so at peace, and somehow, I knew that this was only an illusion. The real Rias was only just starting to show herself.
\end{document}