\documentclass{article}
\begin{document}
Rias has some good news for us. At least, I think it's good news. The only thing I knew was that's he wanted to make an announcement to the group and that to hold off leaving until she sis done.

As I finish packing up my things, I make my way to the front of the desk where my lovely buchou always sits. She's there now, with a very pensive look on her face. It reminds me of the time that we were going to fight Raiser, the way her face looks now. It brings back the cold, almost heartbreaking memories.

"Well, now that everybody is here, I guess I can spread the news." I hadn't even noticed that everyone else had gathered around the same spot I have. Some of the members of the club seemed concerned, like Kiba and Asia. Gasper seemed to be a little too nervous, and Xenovia Akeno seemed relatively interested. I had to admit, I was also curious as to what she wanted to say.

"So, I just got word of a special field trip just for the Occult Research Club!" Rias said with joy.

"What?! Really?! To where?!" everyone cried. Everyone was shocked. It wasn't every day that you heard that the school was giving you an exclusive trip.

"The trip will be an all expense paid 'vacation' package to the beach. The package not only includes a relaxing time at the beach, but we will stay there for the WHOLE weekend," Rias explained. How in the hell does the school have so much money?! That must have cost a fortune! Then again, I don't mind. At least I'll get to see all the girls in their bikinis... As my mind wandered, something just didn't add up. Who gave us this massive deal and why?

"To be honest, I'm not even sure myself, Issei," Rias responded. Shit! Did I say that out loud? "My brother said that he had paid for part of it, but not for the whole package. According to him, he only gave about a quarter of the total cost," Rias explained, "but honestly, who cares! I mean, we get to be at the beach for the whole weekend!" The way she said this reminded me of a child that is eager to play at the playground. I wonder what the hell she means by that? Meh, who cares. At least she seems into it. By the way she's been acting lately, it's a bit of a relief that she is so happy about something.

"Anyway, the trip is scheduled for this weekend. We leave for the beach at around 9 Am so we can get there, unpack, and stay out near the shore the rest of the day."

Everyone cheered, including me. Finally, not only will I get a break from my every weekend, but I'll get to see so much oppai that my eyes will melt. This is gonna be the best trip EVER!

Friday Night:

"So we all know what we're doing, right?"asks Rias.

"Yeah. We have to meet here at 7:30 in the morning tomorrow so we can get on the bus and be at the beach by 9 AM," I responded. Everyone nodded in agreement with the plan I laid out. Rias looked at me rather skeptically.

"Wow, Issei, I didn't think you were paying attention when I told everyone the full plan." By the way she said that, I can only assume that she was shocked by my answer. I could only sigh in grief will everyone laughed at Rias's comment. "But hey, at least you did pay attention to what I said. That means that at least your attention span has gone up," Rias says jokingly.

After that outburst, Rias cleared some details as to where we were going. Apparently, we're going to one of the fanciest beachside hotels in the country and spending 3 days and 3 nights in two suite rooms, all paid for by the school's administration. And while this seems rather odd that the school would have the crap ton of money to pay for it, I ignore it and relish the fact that we have a break for it all for the ENTIRE weekend. Now, what would be first on tomorrows To-Do list? Whose boobs should I grope first? I imagine all of the girls in their bikinis, and the thought itself would almost make me lose it.

"What are you thinking, Issei? You seem to be very pensive recently," said Rias sternly. Crap, not good!

"Uhhh, I was just thinking about the wonderful time we were gonna have there. And of course, what I wanted to do when we are there," I responded.

"Well, from the faces you were making, it looked like you were thinking of something far more... DANGEROUS..." Rias says. The next thing I know, all the girls are on me, with some very serious, almost deadly looks on their faces. Oh, shit. This can't be good. "Issei, you and I will have a serious talk when we get to you place. A REAL serious talk." Crap, I'm screwed!

After that, the girls let up on me, as if knowing that Rias will take care of my "dreams" for good. In a few minutes, Rias discussed the final details about our arrival and what we will do once were there. When she ended the meeting, everyone collected their things and we all left as a group.

Once we got home, I went upstairs to leave my stuff in my room. I don't know how this happened, but in less than 20 seconds, Rias has me pinned to the bed, with my hands above my head. The look on her face was serious, but had a playful undertone to it. Almost as if, she wanted to toy with me.

"Are you going to tell me what had happened in the club room already?" she asked seductively.

"Umm... well... you see...mph!" In that moment, she had rubbed one of her long legs on my inner thigh, close enough to my private area that I can fell tingles running through every inch of my body.

"Tell me, Issei, or you'll feel that...," she said as she did th same thing again, "for a looong time." Shit, what do I do?! I'm pinned! Should I just tell her the truth? Do I even have a choice?

I went back and forth with the idea for a second. I sighed as Irelented, "Well," I said as I turned slightly red. This is gonna be bad.

"Well, what Issei? Spit it out!" said Rias impatiently.

"Well, I was imagining what you and the other girls would look like in just your bikinis for a full weekend." i responded quickly.

After I said this, a light blush began to form on Rias's cheeks. She pulled away slowly, releasing me of her iron grip. Note to self: Do more strength training, I thought as I rubbed my wrists. When I lloked up, I noticed that her cheeks slowly got a rosy tint to them. "Well, arent you a little naughty?" Rias said seductively. "I thought you would have gotten a good look when we fixed the school's pool," she continued.

"Well, I wasnt just thinking about that," I said. "I was alos wondering whoes boobs I'm gonna fondle first..." I said a little absent mindedly. At this, Rias's cheeks turned a deep shade of scarlet. Not only that, but her ears started to get red to.

Then, what she said in response is what got to me, "Whose did you decide on?" she muttered.

"What?" I asked. The question caught me off gaurd. Are you seriously wondering that?

"Whose breasts did you decide to fondle first?" she asked again, a little more firmly, but still in a low voice.

"Well..." I started, "I didn't actually decide yet." And it was true; I had only began to think about whose would feel better, and then they interupted me.

What she did in response also caught me off gaurd. She sat down on my left next to me, then grabbed my arm and clung to me a if I were her pillow. While I liked the sensation of her boobs pressed tightly against my side, I was rather shcoked. Was Rias jealous of the other girls?

Then, as if out of nowhere, I felt my side becoming wet. Wait, where is this water coming from? I look to find that it's Rias. Althoug you can barley see the, there were tears forming right at the brims of her eyes.

"Issei, dont you ever compare me to other girls to me," Rias said. Yup, she's jealous I told myself.

"Well, to be honest, it was more of a debate between you and Akeno, but I was leaning more towards you," I told her. "I mean, after all, you are my main one," I said with a smirk.

Rias's blush only deepened and she raised her posture to give me a kiss. She moved her tounge nesar my teeth, askig for entry. I gracefully let her in, and in a moment, our tounges battled for dominance.

We made out on my bed for a little bit on my bed, adn as we were making out, Asia-chan stepped into the room.

"Issei, what are you doing?" Asia said with a nervous, diappointed tone.

I broke the kiss and looked at her. "Asia, look, it's not what you think," I said hesitantly. Oh crap, not good!

"ISSSSEEEEEI!" Asia screamed, which may have been heard through half the neighborhood. Rias just giggled like a child while I tried to gain all of my hearing back. Okay, Note to self No.2: Do not get caught prefering only one girl. Actully, make that a goal. And so, that's how our adventure to the beach slowly began.
\end{document}