\documentclass{article}
\begin{document}
\emph{"It's a possibility," I told him, "Anyway, can we continue this conversation later?"…}

I woke up with a start. \emph{Shit! I totally forgot!} In everything that happened yesterday I totally forgot to talk to Ddraig. As I try to get into a sitting position, I suddenly feel something squirming to my left. \emph{Please don't let it be who I think it is.}

I turn my head to the left slightly to find Rias trying to clutch to my side. \emph{Oh, God damn it! Not now!} Although I figured that I wasn't completely alone, I was hoping that it was only an awkward hunch. As I scold myself for not figuring that Rias would show up at my bed tonight, I realized that I was caught in a problem: I can't get out of bed.

\emph{Damn, I'm stuck!} While looking at Rias's sleeping form (which despite myself made me nosebleed a little), an idea popped into my head. It was risky, but I figured, \emph{'Hell, let's give it a shot.'}

I twisted my body slightly to the right, grabbing the pillow I had my head on just a moment ago. I grabbed the pillow and slowly slid away from Rias's grasp, trying to not wake her up. Simultaneously, I slid the pillow into the spot that I was in. At the moment that I completely let go of the pillow, Rias brought it down and clutched it close to her naked form. The top of the pillow where my head would have ended up nestled perfectly between Rias's large and voluptuous boobs. \emph{Damn you, Fate! Just damn you!}

In a swift motion, I slid of the front of the bed and slowly stood up so as not to disturb Rias. Then I tiptoed towards the door, pulled it open, stepped out, and closed the door softly behind me. \emph{Phew, that was a close call!} I went down the hall to where the new upstairs bathroom was.

When I opened the door, the first thing I felt was a blast of warm air. And although it wasn't cold inside my house, I still felt a rush of relief of being in the warmth. \emph{Must be the new air conditioning/heating system Rias's brother installed.} 

Ever since the other girls had moved in to the house, Rias's brother Lucifer had been remodeling it. And while I liked my old house, and it still looked like the old house, I still felt that this new house was ten times better. Since the move in, Lucifer had added in two new bedrooms so all the girls didn't have to share a single room, a bathroom upstairs, and a pool with hot tub in the backyard (how he has so much money, I do not know).

So after I did my business (I had to go take a leak anyway), I tried to call Ddraig. "Ddraig, can you hear me?"

"What is it, Partner?" Ddraig asked.

"Hey, umm, so about what we talked about yesterday..." I began. Now that I tried to begin the conversation, I realized that I don't know why I want to talk about it in the first place. I mean, I guess I don't want to face my own fears of being weaker than I already am. I want to help, but I also want to keep my distance from certain dangers.

"You want to know about the Vanishing dragon, huh?" \emph{How did he nail it on the head?} I did want to talk about the Vanishing Dragon, and know what exactly he does. I want to be able to understand why this dragon is s powerful.

"Yeah, and I also wanted to talk about other stuff. But first, what's the deal with the Vanishing Dragon," I asked. I chose to discuss the after affects and the consequences of having this guys Sacred Gear in my right arm.

"Well, he and I go a long way back," he starts. "When the war between Angels, Demons, and Fallen Angels began, bloodshed and destruction was in it's wake. Many other groups took sides with one of the three factions, with humans being one of them," he explains. \emph{Wow, how long have you been alive!?} I wonder in awe. "In time, another completely different battle ensued. But it wasn't between any of the factions, or even on the ground, but in the sky." \emph{What in the hell are you talking about?} "As war raged on, the Kings of the sky battled it out. What about, they may not even remember. Yet, their battle was fierce and destructive. In fact it was so destructive, that the factions had to make a truce in order to defeat us. They fought well, and they chopped the dragon's to bits." At the sound of this, I suddenly got a chill. That does NOT sound too pleasant.

"So what happened? What does this mean for me, and what about the Vanishing Dragon?" Even though I already heard the story once before, I realized that there was a different tone to it. Why did Ddraig sound so hesitant to recount this story?

"Well, we were chopped up into pieces, and our souls were locked into what is now known as the Red Dragon Emperor's Gauntlet and the Divine Dividng Gear, both of which you posses now, at least to some degree." As he said this, I couldn't help but notice that he was apprehensive about telling me all this. \emph{What are you not telling me here?}

"So, what does this have to do with what's going on to me now?" I asked,

"Do you mean the dozing issue?" he asks rather distractedly. "This is just a theory, but I suspect that this gear, when placed into the hands of an ignorant fool (\emph{fuck you, Ddraig!}), it would reduce that person's physical and mental capabilites by about a half of their original ability."

\emph{Well that's just great! Now I'll never be able to protect Rias! I'll just be weaker than before.} "Well, don't think about it like that, partner." I hadn't realized I said this aloud. but I was right. How the hell was I gonna protect Rias if I'm gonna be weaker than before?! What a useless pawn I am, can't even protect my own king! As if out of nowhere, I began to feel tears come out of my eyes. I am useless to everyone in the group, a stupid weak thing that can't even defend himself!

"Issei, is everything alright in there?" Oh crap, I woke up Rias! I didn't realize i was spewing out my thoughts to the room, but now I realized that she heard everything i said. I sat there, with tears in my eyes, wondering how i was gonna help my buchou. "Oh, Issei, I don't know what exactly what is going on here, but I do seriously hope that what you were saying right now was wasn't serious."

In a moment, the tears start streaming from my eyes. "No, their true. If what I am imagining is correct, than I will be good for nothing more than a decoy," I say with disgust. Disgust at myself, for being weak and useless.

"Issei, you are not useless." I l;ook up to find that Rias has tears down her face, except that she's smiling. "You are what makes me whole. I don't know what it was, but from the moment I met you, i have grown to like you to the point that losing you would hurt me. Issei, you are something spwecial to me, and to everyone in the club. If what you say does happen, then we will help you to recover it." At this, the stream of tears coming down my face becomes a flowing river, and I come up to grab hold of my buchou.

I snuggle my head in between her large breasts, and cry my eyes out till I can cry no more. The whole time, Rias was there to comfort me, telling me soothing words as if I were a baby. Even though I couldn't see her, I could tell that she was crying as well. I would feel her tears lightly land on my hair, gentle but still there. I was dreading this would happen again, but somehow knew it was inevitable. I balled like a baby because deep down in my heart, I was afraid of becoming weaker.

When I stopped crying, I shifted my head away from Rias's chest, looked up, and came to see that she was still crying, but had a soft smile on her lips. in a moment, i closed the gap between us and planted a deep kiss on her lips. For a moment, she was shocked, stricken by my impulsiveness. then, a moment later, she returned it with as much fervor and passion as with what I gave her. We were sitting on the floor of the bathroom now, making out in front of the open in that instance, I didn't care who came in and saw us. Because no matter what, Rias would be with me forever. And as long I had her guiding me, i was sure that she would do whatever it took to guide me.

As I broke the kiss, I noticed that I hadn't had a chance to breathe, and I was panting a little to get back to normal. When I saw Rias doing the same, a deep red blush came upon her cheeks. "Well, that was something else," she said a little shyly. "Come on, let's get back to bed. I'm sure we won't want to get up tomorrow morning." As we made our way to my bedroom, I realized that she actually cared. At first, I though she had taken me because she needed that pawn piece. Now, I realize that she had wanted me to be a lot more than just a pawn. All this time, I was hoping to be with her, and when I was, I never truly thought about her in any other way besides the look of lust.

As we enter my room, and lay on my bed, I start to wonder, what now? I mean, sure, I may get weaker, but as long as I have Rias by my side, I know that I will succeed somehow/. Beacsue no matter what, I know that Rias will be there to cheer me on, and to support me as much as she has supported the rest of the group and then some.

So as Rias snuggles into my side, trying to get comfortable, I make myself closer to her, and notice that we are compliments of each other. "Well... isn't that interesting," I say with a slight smirk.

"Oh shut up, you wimp," Rias says jokingly.

In the last few moments of conciousmess, I press my lips onto her temple, and utter the words that have been in the back of my mind since the first day I met her, "I love you, Rias."

Before I closed my eyes, I saw her blush slightly, then heard the words I've always wanted to hear from a girl. "I love you, too, Red Dragon Emperor." And with that, we both drift off to sleep, knowing that we support each other and that the Demon and the Dragon, with a passion brighter than the flames of hell, will stand above the rest and reign supreme.
\end{document}