\documentclass{article}
\begin{document}
It wasn't long after I had "passed out" that the girls woke me up from their floor. I honestly don't know what is wrong with me, and it annoys me to all hell and back. I mean, I'm going to be \textbf{King of the Harems} damn it! I should be able to view any girl in skimpy clothing and bask in all that glory!

\emph{Sigh.} Oh well, its not like it matters now anyway.

Once I recovered, we had all gone beachside and had just a day off out in the beach with the sun. As I was lounging on the beach, watching the girls splash around near the water, I hear my name coming from my right side.

I looked over a bit out of the corner of my eye, and find Rias there, lying on her stomach, a bottle of sun-tan lotion in her hand.

"Oh, Issei?" she says, a smug, playfully seductive tone in her voice.

Goosebumps appeared on my skin, but not from fear or from cold. Rather, its more because she knows my all to well, and she is playing my horny nature like a fiddle.
 
"Y...yes?" I ask, nervous and excited. \emph{God damn it, get a grip, you idiot,} I scream to myself.

"Would you mind helping me out with this lotion? I can never get it on properly on my back," she says, that seductive tone still playing at her lips.

It was those words that triggered the more, ahem, \emph{inappropriate} side of me to go wild. Oh the things I could do to her, if she would give me the chance. \emph{Touching her all over, in areas where I usually don't even get to see...} I'm salivating at the thought, and it's firing me up more than ever.

My face must be giving off what I'm thinking, cause one look on Rias's face is all the info I need to know that this torture is NOT ending anytime soon.

I look to Rias and nod, too nervous and scared to speak for fear of my voice breaking. 

She hands me the bottle of sun-tan lotion, and I get right to work. I squeeze a little bit of the lotion onto my hands, rub it between my palms, and begin near her shoulders. 

The effect on her body seems instant, as shivers seem to go down her body. \emph{Must have been waiting for this moment.} I slowly massage her tense shoulders, make them more maleable. The sigh of bliss and relief that escapes her lips is both cute and divine.

I continue on, steadily inching down her back to below her breats. I gently knead her back muscles, which are suprisingly well toned, even tho I know her wings are a big help in that department. I then decide to do something that would probably land me a good amount of pain. \emph{Fuck it, now's a good time as any}.

I go back up just a couple of inches until my hands were right beside her breat area. \emph{OK, good so far}, I thought. I slowly massage her breats, making sure to be gentle
\end{document}