\documentclass{article}
\begin{document}

As a demon, life can be a hassle. The sun is a bother. I have sleep deprivation. I spend nights on end going to strangers' houses, creating supernatural pacts. My friends get me in trouble for their pervy tendencies. Yet, there are also perks to being a demon. Like being able to use magic, or having strength that is ten timed that of a normal human. Oh, and one last thing, which is really my most favorite part: demon girls lust over me.

Yep. That's right, you heard me. The group of friends that I hang out with, also known as the Occult Research Club, is filled with girls. Really hot and cute demon girls, the kind of girls that happen to appear to you in wet dreams (don't ask me how I know that, I just do). You got that in your head? Good. Now that you can see that just know that a very pervy and scrawny guy like me gets all of that on a day to day basis. Jealous, right?

Anyway, since they all moved in to my house, things have gotten pretty nice. Again, you heard me, and I shit you not. These girls take a shower here, eat here, sleep here, and do anything else they want to do.

Now let me explain a little bit about this situation. The girls live in two separate rooms, split into groups of about three (there are five, do the math). There are two cute girls that I keep my eyes out for, Koneko and Asia. Koneko is the more "experienced" member of the two in the group. She is petite, with white hair and hazel eyes. She seems to have a natural liking of cats (or our "cat-girl"), and is considered the mascot of our school, Kuoh Academy. Normally, she is found eating one thing or another. Where she puts it all is a mystery I have yet to uncover. Then there is Asia-chan. She is also very petite, but is blonde and has green eyes. She, unlike most of the girls in the group, is very innocent in regards to anything pervy. My goal with her is to preserve it as much as possible.

Then there are the three hot beauties of the group. There's Xenovia, the blue haired, yellow eyed angel turned demon (long story I DO NOT want to get in to). She's the more direct and rather blunt of the group, with boobs that are decent for her tall frame. Then there is Akeno, the tall dark haired beauty with purple eyes. Also known as the "Priestess of Thunder" in our group, it would be easy to tell why (I know I found that out pretty quickly). Her figure, including her boob size, is just one of the best in the entire academy.

Finally, there's Rias. This crimson haired beauty is, in my opinion, the best looking girl in the entire academy. She is tall and slender, with that long flowing hair going just past her shoulders. Not only is she hot, but she's smart to boot. her knowledge of the underworld as well as our Earth based knowledge (both street and book smarts!) can rival that of anyone in our little group. Not only that , but she is undoubtedly one of the hottest girls in the entire school. The reason I know all this is because she is the club's \emph{buchou}, or President. To me, she means the world. I would od anything to have those boobs by my side all the time (by the way, did I mention these are also some of the largest boobs in the entire school, along with Akeno's?). For these reasons, and for the simple fact that she saved me from total MURDER at the hands of a fallen angle bitch. She may have been my first date, but my \emph{buchou} Rias is my only true love.
\end{document}