\documentclass{article}
\begin{document}
As soon as Asia yelled, which I swear could be heard down to the next block at least, all the girls came rushing in. Since Rias was still clutching on to me while I was explaining to Asia what was going on, the other girls came bursting into the room. "Asia, what's wrong?" asked Xenovia, unbeknownst to the situation.

"Issei has been cheating on all of us with Rias!" Asia sobbed. The whole scene was painful to watch and I felt really bad about the it. As the girls took a look at the whole scene, a general feeling of anger and jealousy began to surface among everyone present.

"Ara, ara. Issei, what have you gotten yourself into this time?" said Akeno, a devilish (heh) smile playing on her lips, eyes gleaming with jealousy.

"Yeah, Issei! What about everyone else?!" said Koneko. Everyone seemed to stop for a second and looked at Knoneko. \emph{Wait, since when did she gave two shits about what I did?! Aren't I just some mega perv to her?!}, I thought. "Well, if he's gonna be with us, then why not with all of us?" was all Koneko could say, as if she was flooded with embarrassment by the whole ordeal. Hell, I think I saw a blush forming on her cheeks.

On and on, I was the target of some pretty nasty comments. In that whole time, Rias just sat there, observing my every move, listening to everyone argue back and forth. Eventually she seemed to get tired of it, because she then shouted, "Enough!"

Everyone turned silent at this command, almost seemingly forgetting their anger and looked at her. \emph{They may be pissed at us, but she is still their master, and mine, too}, I thought. 

"Look, I'm the one to blame for this whole incident, okay? I was the one who put the moves on Issei and I'm the one who made this whole ordeal happen. Issei was in no way responsible for his actions," Rias explained. \emph{Well, at least in the beginning}, I noted to myself. "Now, everyone just get back to relaxing and enjoying this vacation! We all need this, anyway!" said Rias. The rest of the girls seemed to agree with what she said and decided to leave me be. And although it looked like Rias was being innocent and honest, I don't think that the sly smirk she gave me before she left was an accident.

So there I was, alone in my room, tired as shit after that whole ordeal, and not knowing what to do. \emph{Maybe I should go see if the girls are changing?} Like I said before, I wasn't that much of a perv. I like looking at boobs, but watching girls change as another thing. I have my limits, you know. I waited for about 20 minutes, assuming that's how long they take, I went across the hall to the girls' suite. I knocked on the door, and put my ear to the door. I heard quite a bit of noise because of the sound of the knocks. Sounds of "Are you sure about this?" and "Sure, why not?" came in what sounded like hushed whispers. What the hell are they doing?, I wondered.

"Ok, Issei, you can come in now," came Rias's voice from the door. \emph{How did she know it was me?} As I opened the door, I got a feeling that what was on the other side was something that would either scar me for life, or be so epic that I wouldn't be able to take it. When I finally opened the door, all the girls were there in nothing but these skimpy bikinis. Even Asia! \emph{Damn it, why her?!} In that instant, my body refused to cooperate with my brain, and the next thing I know, I was on the ground, blood gushing from my nose.

"Issei, are you all right?" Asia asked, traces of shock and concern coloring her tone.

"What, was this too much for him to handle?" I heard Xenovia say, disappointed in the reaction.

"Well, we may have overdone it a little," I heard Rias say, in a sort of apologetic tone. In that short little instance, I began to daze out, and no later than that, I passed into the blissful world of slumber, with the girls images in my head.
\end{document}