\documentclass{article}
\begin{document}

\emph{That night, I couldn't sleep well. I was restless, tossing and turning, wanting to know what Rias is feeling. I don't know when I fell asleep, but when I did, I noticed that the only one that came beside me tonight was Rias.}

\emph{In a way, her sleeping form looked so innocent. She looked almost like a pre-teen, maybe 12-14 years old at the most. I mean, I knew she was seventeen, and that people look younger when they sleep, but this was an astoundingly large difference. Not only did she look younger, but she seemed to be so at peace, and somehow, I knew that this was only an illusion. The real Rias was only just starting to show herself.}

As I slid out of bed and began my usual morning routine, what happened last night kept going through my head. And while you may be wondering how this has been in my head, and not the fact that Rias appeared in my bed again (and naked, by the way), trust me, I almost nose bled all over my sheets. Yet, while looking at her and how she seemed so at peace, wondering what it was that bothered her mad my body stop the already natural reaction.

By the time I got out of the shower, the side where Rias was laying so peacefully just a moment before was now empty. \emph{She must have gotten up to get ready for school}, I told myself. And while I wasn't 100\% sure that was true, I settled on the conclusion and gathered my things.

Just as I was about to leave my room, a voice suddenly appeared. "Partner," Ddraig said. "I wanted to converse with you. Do you have a minute?"

"What is it, Ddraig? It's been a while since we talked." As I said these words, I truly felt a sense of distance. I mean, not only is he physically far away (in another dimension that is somehow connected to my Sacred Gear), I haven't talked with him since my battle with Levi (more about that later), and that was just to let him know what I really wanted to do with my life. As I reminisce, I realize that Ddraig had been trying to get my attention. "What, I'm sorry. I dozed out for a second. What was up?"

"That's exactly what I wanted to talk about," he remarked, "You seem to be dozing out a lot lately. I've been noticing that ever since we ended the battle with the Vanishing dragon". By that, he meant Levi, my now rival destined to fight me at some point. "What is really going on here, partner?"

Although this wasn't really the time to become my therapist (I mean, the girls are waiting for me downstairs, by the sounds I can pick up), he was right. This "dozing off" has started since I finished my battle with Levi, more specifically after I fused Levi's Sacred Gear with my own. And if I'm going to be quite honest, it's starting to really freak me out. 

"I don't really know," I told Ddraig, "I just feel like my brain power isn't completely there."

"Oh, really? Since when did you have a brain?" I heard Ddraig mutter.

"Screw you Ddraig!" I told him, "I meant that I feel that my brain is on overload," I tried to explain. "It's like my brain power has been sliced in half!"

"Hmmmm…" I heard Ddraig respond, "Maybe it was the effect of merging the Vanishing Dragon's Gear," Ddraig suggested.

"It's a possibility," I told him. "Anyway, can we continue this conversation later? I need to go and get some breakfast so I can head to school." \emph{Not to mention see the girls' outfits!}

It took a while, but eventually Ddraig said he'll talk to me later. As I gathered my composure, I arrived at the kitchen table. "Where were you?" asked mom. "We were all waiting for you to come down and eat, but we had to go on without you!" As she said this, she was gesturing towards the girls and my dad, too.

In a way, I felt kind of bad. I mean, I could have - no, should have - been eating with the girls and I didn't! Yet at the same time, there was this revelation. Yes, I have been zoning out more than normal, and yes, it looked weird, but at least I knew that it was happening, and that I needed to stop. "I'm sorry, mom. It won't happen again," I said so as not to seem suspicious.

"Well, okay Issei. At least you apologized. Now get your breakfast and take it with you out the door. You and your friends are going to be late for school." With that, she whisked us out the door and to the front lawn.

As we walked, I began eating my breakfast sandwich (way to go American, mom), and on the way, we meet up with Gasper and Kiba. I decide to go in front of them just so I don't bump into them if I get distracted. In a matter of moments, I hear that someone has joined me at the front of the pack. I turn to my right and find that it's Rias. "Are you enjoying that breakfast Issei?" she asked with a rather curious tone.

"What?" I asked. \emph{What's going on here, this isn't like Rias.}

"Are you enjoying the breakfast?" This question had me stumped. I mean, the answer was obvious, yeah I was. But under the surface, this was so much unlike Rias's character. She normally wouldn't ask such a random question.

"Yeah, I thought it was good," I said as I took the last bite. Again, I find it very odd that she would ask me about something so random. Then I saw it, the weird glimmer that appeared in her eyes. Then, the terror in them made it just scarier. \emph{What's wrong, buchou?}

"Well, that's good. You know, me and Asia made them with your mom, right?" she remarked, "So thanks for the praise." She said this with a sort of confused, even distracted tone. Now, usually, this tone is justifiable because she usually has her own problems to worry about (especially way back when with Raiser and the whole Factions business), but this was different. She was a little too distracted, as if it was something that was keeping her awake at night.

"Buchou, are you okay? You've been kind of off". I knew this question sounded kind of weird, but at least I might get something out of it.

"Yeah, I'm okay. Just a little tired, that's all." And with that, she dismissed my question. In a way, I was relieved she hadn't said anything else. I mean, I didn't know what to expect, so it made me worry about what she would have said. Yet, at the same time, I wanted to know and see if I could help. I mean, Rias has done so much for me. Hell, she brought me back from the dead! So I was left there in wonder.

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

As the club meeting came to a close, it was clear the Rias was a little too distracted than normal. She didn't seem to have her usual drive, and her teasing was less than usual (I guess that was more on my own part, but whatever). I don't know, but I suddenly feel that I have to help buchou.

"Hey, buchou?" I ask rather hesitantly. \emph{All right, let's do this!}

"Yes, Issei, what is it?" she asks, curiously looking at me. \emph{Okay, time to ask what I want to ask, No backing down now!}

"Ummm… Can I talk to you before you leave? " \emph{Okay, here we go.}

"Sure, Issei, let me just gather my things so we can leave right after." In a flash, she had gathered all of her papers and stuff and put them neatly in her bag. \emph{Oh Rias, how cute is that}. "So, what did you want to talk to me about?" Rias asks.

"Well, I noticed you haven't been your usual self all day. I mean, you haven't been the Rias I meet all those months ago. I want to know, what's been haunting your mind all this time?" I ask, a little unsure of myself.

I don't know what I said to set her off, but in a few moments, tears started to flow out of her eyes. Then, she ducked her head, as if in shame. "What's wrong, buchou, was it something I said?" I ask again.

"No, no, it wasn't what you said, Issei. I guess it's more of the fact you would ask me that," she responded. \emph{Huh? What in the hell are you talking about, Rias?} "The fact that you care about what is actually bothering me that is making me cry. It wasn't anything you said, just the thought behind it" she continued, "And honestly, it's a lot of things that have been bothering me. The one thing that has me on edge, though, is YOU."

"Huh, what do you mean buchou?" \emph{Okay, what in the hell is she talking about? What does she mean by mean by ME?}

"I mean, I guess it's your condition that trouble me," she says, the tears now streaming down her face. "I didn't want to say, because I thought that it was a ridiculous fear, because you grown to be so skilled. Yet, you also have taken too many risks for me. I just don't want to see you…" she stops. Then again, I didn't need her to finish. I knew what she was going to say. \emph{I don't want to see you die for me.}

"Look Rias, I don't know what you think of me, and I don't want to guess. The fact of the matter is that the last thing I want for you is this, "I said, gesturing to her sobbing figure, "Look, just I have put my life on the line for you, you have put your for me and for the rest of the group. I mean, I owe you my life. If it wasn't for you, I really WOULD be dead. In a way, it's the least I could do to repay the kindness you've shown me," I tell her.

This seems to have lifted a weight off her shoulders, and she starts to bawl into my chest. Somehow though, I know that these tears have turned from tears of worry to tears of joy. Joy over having been thanked, for being a recognized part of the team, She seems to have cried out all her worries and frustrations right in my arms, and by the time she's done, her eyes are puffy and red. No, not red, scarlet. \emph{Like her hair.}

"Thank you, Issei. Thank you for being there for me," she says.

As we leave the clubhouse (yeah, don't judge me), I know that this isn't the end of it. I know now that Rias truly cares about me, and as such, I will do whatever it takes to defend her and my other friends. Even if it costs me my life, I'll be happy knowing that Rias is safe and sound. I just hope that Rias is fine with it, too.

\end{document}